14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-19 rules/rules19.tex
Rules: Competitive divisions.

% The time limit~$T$ will be 40~minutes of wall-clock time per solver/benchmark
% pair in the \maintrack, \inctrack and \ucoretrack, \todo{12 hours} in the
% \challtrack, and \todo{40 + 5 as in Unsat core}~minutes in the \mvaltrack \footnote{The time limit may be
% adjusted once we know the number of competition entrants and eligible
% benchmarks.}  Solvers that take more than this time limit will be killed.
% Solvers are allowed to spawn other processes; these will be killed at
% approximately the same time as the first started process.

@@

\header{Aborts and unparsable output.}
%
Any \texttt{success} outputs will be ignored.  Solvers that exit
before the time limit without reporting a result (e.g., due to
exhausting memory or crashing) \emph{and} do not produce output that
includes \texttt{sat}, \texttt{unsat} or \texttt{unknown} will be
considered to have aborted.

@@

The disk space and memory limits for the incremental track are the
same as for the \maintrack (see Section~\ref{sec:exec:single}).

@@

In order to perform this unsatisfiability check, the organizers will use a
selection of SMT solvers that participate in the \maintrack of this
competition.  For each division, the organizers will use only solvers that have
been sound (i.e., not produced any erroneous result) in the \maintrack for
this division.  The unsatisfiability of a produced unsatisfiable core is
refuted if the number of checking solvers whose result is \texttt{sat} exceeds
the number of checking solvers whose result is \texttt{unsat}.  The time limit
for checking unsatisfiable cores is yet to be determined, but is anticipated to
be around 5 minutes of wall-clock time per solver.

@@

@@

\todo{time limit}
The \challtrack will include both incremental and single query benchmarks and
it will follow the same rules as the \inctrack and  \maintrack, respectively
with two exceptions: benchmark selection and the time limit. The track will
run on challenging industrial benchmarks provided by the community. This year,
the \challtrack will include both incremental and single query benchmarks in the
following logics QF\_BV, QF\_ABV and QF\_AUFBV. The complete list of benchmarks
along with instructions on how to access them will be provided on the SMT-COMP
website as soon as the benchmarks are released.

@@

@@

\todo{Aina: We do not run non-competitive divisions.}

@@

\subsection{Competitive divisions}

Scores will be computed for all solvers and divisions.  However,
winners will be declared only for \emph{competitive} divisions.  A
division in a track is competitive if at least two substantially
different solvers (i.e., solvers from two different teams) were
submitted.  Although the organizers may enter other solvers for
comparison purposes, only solvers that are explicitly submitted by
their authors determine whether a division is competitive, and are
eligible to be designated as winners.

>>>>

\header{Aborts and unparsable output.}
%
Any \texttt{success} outputs will be ignored.  Solvers that exit
before the time limit without reporting a result (e.g., due to
exhausting memory or crashing) \emph{and} do not produce output that
includes \texttt{sat}, \texttt{unsat}, \texttt{unknown} or other track
specific output as specified in the individual track sections e.g. unsat
cores or models, will be considered to have aborted.

@@

@@

@@

In order to perform this unsatisfiability check, the organizers will use a
selection of SMT solvers that participate in the \maintrack of this
competition.  For each division, the organizers will use only solvers that have
been sound (i.e., not produced any erroneous result) in the \maintrack for
this division.  The unsatisfiability of a produced unsatisfiable core is
refuted if the number of checking solvers whose result is \texttt{sat} exceeds
the number of checking solvers whose result is \texttt{unsat}.

@@

\header{Time Limit.}
This track will use a wall-clock time limit of 40 minutes per solver/benchmark
pair. The time limit for checking unsatisfiable cores is yet to be determined, but is anticipated to
be around 5 minutes of wall-clock time per solver.

@@

The \challtrack will include both incremental and single query benchmarks and
it will follow the same rules as the \inctrack and  \maintrack, respectively
with two exceptions: benchmark selection and the time limit. The track will
run on challenging industrial benchmarks provided by the community. This year,
the \challtrack will include both incremental and single query benchmarks in the
following logics QF\_BV, QF\_ABV and QF\_AUFBV. The complete list of benchmarks
along with instructions on how to access them will be provided on the SMT-COMP
website as soon as the benchmarks are released.

\header{Time Limit.}
This track will use a wall-clock time limit of 12 hours per solver/benchmark
pair.

@@

\header{Time Limit.}
This track will use a wall-clock time limit of 40 minutes per solver/benchmark
pair. The time limit for checking the satisfying assignment is yet to be
determined, but is anticipated to be around 5 minutes of wall-clock time per solver.

@@

\header{Competitive Divisions.}
A division in a track is competitive if at least two substantially
different solvers (i.e., solvers from two different teams) were
submitted.  Although the organizers may enter other solvers for
comparison purposes, only solvers that are explicitly submitted by
their authors determine whether a division is competitive, and are
eligible to be designated as winners.
We will \textbf{not} run \emph{non-competitive} divisions.

@@
